Programming Assignment 2

### 2015-04-02 paper.tex
Update paper.tex

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.

\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

@@

These errors are likely due to bad encoding. Our group noticed that large
images with thin outlines lost information when being resized to a smaller 
image. Also most of our outlines were collected from the internet. These
outlines were incredibly diverse and perhaps the details of each image were
simply 'drowned' out in the diversity of the images. If we standardized our 
input we would have likely seen better results.

@@

\subsection{Performance}
Our LVQ had some pretty good performance but also some poor performance.  When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.  It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.  However the other 79\% of animals were correctly classified.  Aircraft were a little trickier.  With 66\% overall correct classification, most aircraft were classified as Jetfighters. All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.  Sea-fareing objects were not as great.  Not a single image was classified as a ship.  However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
\begin{itemize}
\end{itemize}

\subsection{Sensitivity}
Being a feed-back network, the LVQ did fairly well to adapt to small amounts of noise. Because the centroids themselves had noise, the LVQ did the best overall out of all implementations. Being able to try over and over to get the actual centroid from a distorted image really helped aleviate a lot of the problems that came with the noise.

>>>>

\subsubsection{Classifications}
The classifications used by BAM were encoded as orthogoal vectors of length 6.
Each class 'supersection' had a total of 3 classes. The animal supersection
includes Dogs, Elephants, and Giraffes. The Plane supersection includes Biplanes,
Jets, and Airbuses. Finally the Marine supersection includes Ships, Submarines,
and Whales. Each supersection is treated separately. The encodings for Animals
are used again in Planes and Marines. This was to make the classification
encodings as simple yet distant as possible.
\subsection{Performance}
The Bidirectional Associative Memory implementation performed rather poorly.
Most of the associations were directed towards a specific centroid, resulting
in at least 1 'class' performing extremely well. The results of our
experiment are as follows.
Animal Results:
    Dog:
        7 Correctly Classified
        3 Incorrectly Classified
    Elephant:
        1 Correctly Classified
        9 Incorrectly Classified
    Giraffe:
        0 Correctly Classified
        9 Correctly Classifed
Plane Results:
    Biplane:
        0 Correctly Classified
        10 Incorrectly Classified
    Jet Results:
        5 Correctly Classified
        5 Incorrectly Classified
    Airbus Results:
        0 Correctly Classified
        7 Incorrectly Classified
Marine Results:
    Ships:
        0 Correctly Classified
        5 Incorrectly Classified
    Submarine Results:
        8 Correctly Classified
        0 Incorrectly Classified
    Whale Results:
        3 Correctly Classified
        7 Incorrectly Classified

@@

@@

\subsection{Performance}
Our LVQ had some pretty good performance but also some poor performance.  When testing animals against eachother (dogs, elephants, and giraffes) the network maintained a fairly consistent classification.  It returned 21\% false negatives by misclassifying 4 dogs and 2 elephants, all as giraffes.  However the other 79\% of animals were correctly classified.  Aircraft were a little trickier.  With 66\% overall correct classification, most aircraft were classified as Jetfighters. All ten jet fighters were correctly classified and 9 passenger aircraft and biplanes misclassified.  Sea-fareing objects were not as great.  Not a single image was classified as a ship.  However, 70\% of whales were correctly classified and all of the submarines were correctly classified.
Animal Results:
\begin{itemize}
    \item Dog:
    \begin{itemize}
        \item 6 Correctly Classified
        \item 4 Incorrectly Classified
        \end{itemize}
    \item Elephant:
    \begin{itemize}
        \item 8 Correctly Classified
        \item 2 Incorrectly Classified
        \end{itemize}
   \item Giraffe:
   \begin{itemize}
        \item 9 Correctly Classified
        \item 0 Correctly Classifed
        \end{itemize}
\end{itemize}
Plane Results:
\begin{itemize}
    \item Biplane:
    \begin{itemize}
        \item 7 Correctly Classified
        \item 3 Incorrectly Classified
        \end{itemize}
    \item Jet Results:
    \begin{itemize}
        \item 10 Correctly Classified
        \item 0 Incorrectly Classified
        \end{itemize}
    \item Passenger Results:
    \begin{itemize}
        \item 1 Correctly Classified
        \item 6 Incorrectly Classified
        \end{itemize}
\end{itemize}
Marine Results:
\begin{itemize}
    \item Ships:
    \begin{itemize}
        \item 0 Correctly Classified
        \item 5 Incorrectly Classified
        \end{itemize}
    \item Submarine Results:
    \begin{itemize}
        \item 8 Correctly Classified
        \item 0 Incorrectly Classified
        \end{itemize}
    \item Whale Results:
    \begin{itemize}
        \item 7 Correctly Classified
        \item 3 Incorrectly Classified
        \end{itemize}
\end{itemize}        
\subsection{Sensitivity}
Being a feed-back network, the LVQ did fairly well to adapt to small amounts of noise. Because the centroids themselves had noise, the LVQ did the best overall out of all implementations. Being able to try over and over to get the actual centroid from a distorted image really helped aleviate a lot of the problems that came with the noise.
